Make any stupid plot you want

### 2020-12-09 draft/sections/math.tex
what is visual mapping?

\subsubsection{Sheaf: Subset}
$\Gamma(E)$ is the space of all points in $F$ returned by $\sigma$; therefore the points being visualized in a streaming or animation example can be considered a subset that lives on base space $U \subset K$ with the same fiber $F$
\begin{equation}
    \begin{tikzcd}
        \iota^\ast E \arrow[r, hook] \arrow[d]                                                                       & E \arrow[d, bend right]                       \\
        U \arrow[r, "\iota" description, hook] \arrow[u, "\iota^\ast \sigma" description, bend right, shift right=2] & K \arrow[u, "\sigma" description, bend right]
    \end{tikzcd}    
\end{equation}
where $\iota^*E$ and $\iota^*\sigma$ are $E$ and $\sigma$ restricted to points $k \in U \subset K$.

% add U ^ V + intersection to get section on union which is condition of sheafs.

@@

where $\rho: H \rightarrow S$ is mapping from a mathematical encoding of the image to pixels on the screen.

For a physical screen display, the fiber $D$ encodes position and color of the visual elements as $\mathbb{R}^{7}$:

\begin{equation}
    \mathbb{R}^{7} = \{X, Y, Z, R, G, B, A\}
\end{equation}
where the pixel $p \in H$ has the fields $\{x, y, z, r, g, b\}$. In the case of 2D screens, the predisplay space is a trivial fiber bundle $H=\mathbb{R}^{7}\times S$.

To draw an image, a region $p \in H$ is inverse mapped into a region $s \in S$
\begin{equation}
s = (\rho_{x}^{-1}(X(p)), \rho_{y}^{-1}(Y(p)))
\end{equation}

such that the rest of the fields in $\mathbb{R}^{7}$ are then integrated over $S$ to yield the remaining fields in $p$
\begin{align}
    R(p) &= \oint_s \rho_R(s)ds^{2}\\
    G(p) &= \oint_s \rho G(s)ds^{2}\\
    B(p) &= \oint_s \rho B(s)ds^{2}
\end{align}

@@

\subsection{Artist}
The artist is a mapping from the $\Gamma(E)$ space of all datasets with a shared $F$ and $K$ to a pre-render space $H$ with display target properties $D$ and visualization structure $S$.

@@

\subsubsection{Screen to Data}
%%diagram: [data] -Tau->[RGVXYZ]
%%%            \ /\ / 
\begin{equation}
    \begin{tikzcd}
        E \arrow[d, "\pi" description] & H \arrow[d, "\pi" description]                                                 \\
        K \arrow[u, "\sigma" description, bend right] & S \arrow[l, "\xi" description] \arrow[u, "\rho" description, bend right]
    \end{tikzcd}
\end{equation}
The pullback $\xi$ on $S \rightarrow K$ means that $ r \in E$ can be mapped to from a simplex in $S$
\begin{equation}
    \begin{tikzcd}
        \xi E \arrow[rr, "\tau" description] \arrow[rd, "\xi \sigma" description, bend right] &                          & H \arrow[ld, "\rho^{-1}"] \\
                                                                                              & S \arrow[lu, bend right] &                          
        \end{tikzcd}
\end{equation}

@@

Each point $s$ in the display space $H$, the mark it belongs to can be found by mapping $s$ back to $K$ via the lookup on S described in section~\ref{sec:display} then taking $\xi(s)$ back to a point on $k \in K$ which lies on the connected component $J \subset K$. To got back to the display space $H$  from the simplacial complex $J$ of the signifier implanted in the mark, the inverse image of $J \in S, \xi^{-1}(J)$ is pushed back to $S$, and then  $\rho(\xi^{-1}(J))$ maps it into $R^{7}$.

\subsubsection{Channels}
Acts on different parts of F, types means measurement groups , can be broken out so 
%%tau(E_{u} in E)
Tau can preserves the measurement type properties (group scales)

@@

Tau is fully flexible and can do whatever; knows about fiber \& neighborhood of fiber. Can in theory approximate hatching/dashing/etc can be approximated w/ functions and neighborhood of k.

%%hatches can either grow the R space or function

>>>>

\subsubsection{Sheaf: Subset}

$\Gamma(E)$ is the space of all points in $F$ returned by $\tau$; therefore the points being visualized in a streaming or animation example can be considered a subset that lives on base space $U \subset K$ with the same fiber $F$
\begin{equation}
    \begin{tikzcd}
        \iota^\ast E \arrow[r, hook] \arrow[d]                                                                       & E \arrow[d, bend right]                       \\
        U \arrow[r, "\iota" description, hook] \arrow[u, "\iota^\ast \tau" description, bend right, shift right=2] & K \arrow[u, "\tau" description, bend right]
    \end{tikzcd}    
\end{equation}
where $\iota^*E$ and $\iota^*\tau$ are $E$ and $\tau$ restricted to points $k \in U \subset K$.

%not sure what's supposed to happen w/ sheafs here
% add U ^ V + intersection to get section on union which is condition of sheafs.

@@

where $\rho: H \rightarrow S$ is mapping from a mathematical encoding of the image to a region $xy$ on the screen that the renderer then maps to pixel space.

For a physical screen display, the fiber $D$ encodes position and color of the visual elements as $\mathbb{R}^{7} = \{X, Y, Z, R, G, B, A\}$, where the patch $xy$ is a region in $H$ that we query into $S$ to get values that we integrate into an $\{r, g, b\}$ value. In the case of 2D screens, the predisplay space is a trivial fiber bundle $H=\mathbb{R}^{7}\times S$.

To draw an image, a region  $H$ is inverse mapped into a region $s \in S$ where $s$ is the inverse mapping from pixel to region on $s = \rho^{-1}_XY(xy)$ such that the rest of the fields in $\mathbb{R}^{7}$ are then integrated over $s$ to yield the remaining fields in $p$
\begin{align}
    R(p) &= \oint_s \rho_R(s)ds^{2}\\
    G(p) &= \oint_s \rho_G(s)ds^{2}\\
    B(p) &= \oint_s \rho_B(s)ds^{2}
\end{align}

@@

\subsection{Artist}
What is A supposed to preserve?

The artist is a mapping from the $\Gamma(E)$ space of all datasets with a shared $F$ and $K$ to a pre-render space $H$ with display target properties $D$ and visualization structure $S$.

@@

@@

Each point $s$ in the display space $H$, the mark it belongs to can be found by mapping $s$ back to $K$ via the lookup on S

then taking $\xi(s)$ back to a point on $k \in K$ which lies on the connected component $J \subset K$. To got back to the display space $H$  from the simplacial complex $J$ of the signifier implanted in the mark, the inverse image of $J \in S, \xi^{-1}(J)$ is pushed back to $S$, and then  $\rho(\xi^{-1}(J))$ maps it into $R^{7}$.

\subsubsection{Channels}
The function $rho: S \rightarrow H$ is composed of subfunctions that are dependent on the prerender fiber $D$. In the case of a screen
\begin{equation}
    \rho (\alpha, \beta) = (\rho_X(\alpha, \beta), \rho_Y(\alpha, \beta), \rho_Z(\alpha, \beta), \rho_B(\alpha, \beta), \rho_G(\alpha, \beta), \rho_B(\alpha, \beta), \rho_A(\alpha, \beta))
\end{equation}

where $(\alpha, \beta)$ are coordinates on $S$. The function $Q$

\begin{equation}
    \begin{tikzcd}
        \Gamma(\theta) \arrow[rr, "{Q(\nu_{0}(c),\ldots,\nu_n(c))}"] &  & {\rho_X, \rho_Y, \rho_Z, \rho_R, \rho_B, \rho_G, \rho_A}
    \end{tikzcd}
\end{equation}

% complex columns are combined to \nu

%% \nu is structure preserving if  E->E  & H->H under nu. \phi can be one of the scales in Stevens

% concrete example of \nu as one of our encodings, if artist is faithfully preserving 
% if was fiber, trans on fiber bundle. we require that nu goes to visual side that can support same translation  - work through some examples : if an artist wanted to preserve, this is what it would have to do - for example relations, interval

@@

 Can in theory approximate hatching/dashing/etc can be approximated w/ functions and neighborhood of k.
